SHARP II: Dark Matter Substructure, Gravitational Lens Flux Ratio Anomalies, and the Case of B1555+375: Beware the Effect of Edge-on Disks

### 2015-04-27 papers/B1555_EdgeOn/B1555_letter.tex
quick change from Matt's comments
In bold form

It was first suggested by \citet{Mao1998} that flux ratio anomalies
observed in radio loud multiple images of lensed quasar could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are not sensitive to micro lensing from
stars nor dust extinction. This makes flux ratio anomalies a promising
tool to detect dark matter substructures \citep{Dalal2002, N13}.  At
present, the amount of substructure derived from flux ratio anomalies
is in disagreement with predictions from numerical simulations, with
the former requiring a larger fraction of mass in substructure than
expected \citep{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure.
%
An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

@@

The B1555+375 system was observed using the NIRC2 camera on the Keck 2
Telescope on the night of 2012 May 16 UT.  The adaptive optics system
was used, with the corrections derived from the laser guide star and a
$R$=14.4 tip-tilt that was located 45$^{\prime\prime}$ from the lens
system.  The ``narrow camera'' mode was used, giving a field of view
of roughly 10$^{\prime\prime}$\ on a side and a pixel scale of 10~mas.
Six dithered 300~s exposures were obtained in $K^{\prime}$ band.  The
data were reduced with the standard SHARP pipeline, which is a
python-based package that is a refinement of the process described in
\citet{Auger_EELS1}.  A cutout of the final reduced image is shown in
Fig.~\ref{fig:multiband} and again in Fig.~\ref{fig:merlin} with
contours from the MERLIN radio observations of \citet{Marlow99}
overlaid.  There are several notable features in the Keck AO data.
These include the nearly complete lack of emission associated with the
B and D lensed images, as can be seen by comparing the radio contours
to the $K^\prime$-band emission, and faint but clearly visible
emission from what appears to be an edge-on lensing galaxy.

>>>>

It was first suggested by \citet{Mao1998} that flux ratio anomalies
observed in radio loud multiple images of lensed quasar could be
interpreted as a telltale sign of the presence of substructure in lens
galaxies.  Indeed, small perturbations in the gravitational potential
are sufficient to cause flux ratio anomalies in strong lensed systems
\citep{Bradac02}.  Moreover, unlike in the optical or infrared, in the
radio band, lensed images are not sensitive to microlensing from
stars nor dust extinction. This makes flux ratio anomalies a promising
tool to detect \textbf{and measure} dark matter substructures \citep{Dalal2002, N13}.  At
present, the amount of substructure derived from flux ratio anomalies
is in disagreement with predictions from numerical simulations, with
the former requiring a larger fraction of mass in substructure than
expected \citep{Xu14}. While this could be the result of small sample
statistics, it could also be an indication that flux ratio anomalies
have a different origin than substructure.
%
An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein rings
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

@@

The B1555+375 system was observed using the NIRC2 camera on the Keck 2
Telescope on the night of 2012 May 16 UT.  The adaptive optics system
was used, with the corrections derived from the laser guide star and a
$R$=14.4 tip-tilt \textbf{star} that was located 45$^{\prime\prime}$ from the lens
system.  The ``narrow camera'' mode was used, giving a field of view
of roughly 10$^{\prime\prime}$\ on a side and a pixel scale of 10~mas.
Six dithered 300~s exposures were obtained in $K^{\prime}$ band.  The
data were reduced with the standard SHARP pipeline, which is a
python-based package that is a refinement of the process described in
\citet{Auger_EELS1}.  A cutout of the final reduced image is shown in
Fig.~\ref{fig:multiband} and again in Fig.~\ref{fig:merlin} with
contours from the MERLIN radio observations of \citet{Marlow99}
overlaid.  There are several notable features in the Keck AO data.
These include the nearly complete lack of emission associated with the
B and D lensed images, as can be seen by comparing the radio contours
to the $K^\prime$-band emission, and faint but clearly visible
emission from what appears to be an edge-on lensing galaxy.
